Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

\def\vgap{\vspace{1mm}}
\def\extraspacing{\vspace{2mm} \noindent}
\def\figcapup{\vspace{-2mm}}
\def\figcapdown{\vspace{-3mm}}

@@

        \item Consider any a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v) \in \J_1$. Let $r'_i$ ($i \in [k-2])$ be the trimmed rectangle of $r_i$, and set $\bm{t} = (r'_1, r'_2, ...,$ $r'_{k-2})$. Then, we must have (i) $\bm{t} \in \J(R_1', R'_2, ..., R'_{k-2})$, and (ii) $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$.

@@

\extraspacing {\bf Sets $\bm{R^*_1, R^*_2, ..., R^*_{k-2}}$.} Fix any $i \in [k-2]$. Define for each $r' \in R_i'$:
\myeqn{
    \maxtop(r') &=& \max_{\bm{t} \in \J(R'_1, ..., R'_{k-2}): \gbot(\bm{t}) = r'} \ytop(B_\bm{t}). 
    \label{eqn:hv:type1:maxtop}
}
We set $\maxtop(r')$ to $-\infty$, if no $\bm{t} \in \J(R'_1, ..., R'_{k-2})$ has $r'$ as the $\gbot(\bm{t})$. When $\maxtop(r') \ne -\infty$, assuming $r' = [x_1, x_2] \times [y_1, y_2]$, we introduce a rectangle
\myeqn{
    r^* &=& [x_1, x_2] \times [y_1, \maxtop(r')]. \label{eqn:hv:type1:topsliced}
}
and call it the {\em top-sliced rectangle} of $r'$.

@@

Next, we construct from $R_i'$ a new set of rectangles: 
\myeqn{
    R^*_i = \set{r^* \mid r' \in R_i' \text{ and its top-sliced rectangle $r^*$ exists}}. \label{eqn:hv:type1:R*}
}
In Appendix~\ref{app:hv:type1}, we show how to compute produce $R^*_1, ..., R^*_{k-2}$ together in $O(n + k \cdot \out)$ total time.

>>>>

\def\vgap{\vspace{1mm}}
\def\extraspacing{\vspace{2mm} \noindent}
\def\figcapup{\vspace{-2mm}}
\def\figcapdown{\vspace{-4mm}}

@@

        \item Consider any $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v) \in \J_1$. Let $r'_i$ ($i \in [k-2])$ be the trimmed rectangle of $r_i$, and set $\bm{t} = (r'_1, r'_2, ...,$ $r'_{k-2})$. Then, we must have
        \myitems{
            \item $\bm{t} \in \J(R_1', R'_2, ..., R'_{k-2})$;
            \item $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$.
        }

@@

\extraspacing {\bf Sets $\bm{R^*_1, R^*_2, ..., R^*_{k-2}}$.} Fix any $i \in [k-2]$. Define for each $r' \in R_i'$:
\myeqn{
    \maxtop(r') &=& \max_{\bm{t} \in \J(R'_1, ..., R'_{k-2}): \gbot(\bm{t}) = r'} \ytop(B_\bm{t}). 
    \label{eqn:hv:type1:maxtop}
}
We set $\maxtop(r')$ to $-\infty$ if no $\bm{t} \in \J(R'_1, ..., R'_{k-2})$ has $r'$ as the $\gbot(\bm{t})$. When $\maxtop(r') \ne -\infty$, assuming $r' = [x_1, x_2] \times [y_1, y_2]$, we introduce a rectangle
\myeqn{
    r^* &=& [x_1, x_2] \times [y_1, \maxtop(r')]. \label{eqn:hv:type1:topsliced}
}
and call it the {\em top-sliced rectangle} of $r'$.

@@

Next, we construct from $R_i'$ a new set of rectangles: 
\myeqn{
    R^*_i = \set{r^* \mid r' \in R_i' \text{ and its top-sliced rectangle $r^*$ exists}}. \label{eqn:hv:type1:R*}
}
In Appendix~\ref{app:hv:type1}, we show how to compute $R^*_1, ..., R^*_{k-2}$ altogether in $O(n + k \cdot \out)$ total time.
